\documentclass[10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{url}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}

\title{\textbf{MeasureMatch-Bench}\\\large arXiv Endorsement Brief (2 pages)}
\author{Piyush Jagadish Bag\\Independent Researcher · ECAD validation and test automation\\piyushbag4@gmail.com}
\date{July 2026 — draft v0.1}

\begin{document}
\maketitle

\section*{Problem}
Post-silicon validation teams archive thousands of instrument exports (PSU, thermal, fan, throughput) under inconsistent product aliases and mixed CSV/TXT formats.
Finding one metric slice can take days of manual search.
There is no public benchmark for \emph{entity resolution + retrieval} over such corpora at validation scale.

\section*{Gap (one minute)}
\begin{itemize}
  \item \textbf{TokenPowerBench} --- LLM \emph{inference} power, not lab measurement files.
  \item \textbf{CVDP / VERT / FIXME} --- RTL and verification LLM tasks, not measurement archives.
  \item \textbf{Aerospace LLM+KG case study} (De Santis et al., arXiv:2408.01700) --- not an open multi-task harness.
\end{itemize}

\section*{Contribution}
\textbf{MeasureMatch-Bench}: 24 synthetic corpora ($\sim$6{,}000 files, 46 scenario types) with gold labels for:
\begin{enumerate}
  \item[T1] Product identity resolution (alias $\rightarrow$ canonical SKU)
  \item[T2] Format detection + normalization
  \item[T3] Scenario-targeted retrieval (product + scenario $\rightarrow$ file + value)
  \item[T4] Cross-corpus QA
\end{enumerate}
Harness v0.1.0 + rule baseline R0; extension points for embedding and Qwen2.5-3B-Instruct pipelines.

\section*{Artifacts (live)}
\begin{tabular}{@{}ll@{}}
\toprule
Resource & URL \\
\midrule
GitHub & \url{https://github.com/piyushbag/measure-match-bench} \\
Harness & \texttt{python3 eval/run\_eval.py --split test --pipeline R0} \\
Significance doc & \texttt{docs/why-measure-match-bench.md} \\
\bottomrule
\end{tabular}

\section*{Sample R0 results (test split, 20 corpora)}
T1 accuracy 100\%; T3 retrieval@1 87.2\%; T4 value score 95.9\% (harness v0.1.0, 2026-07-04).

\section*{Endorsement ask}
I plan to submit to \textbf{arXiv cs.AR} (cross-list cs.SE) as a preprint before ITC 2027 Track~B.
If you are a cs endorser and this fits your endorsement neighborhood, I would appreciate an endorsement for submission.

\vspace{0.5em}
\noindent\textbf{Full paper PDF} available on request; this brief is the default attachment.

\end{document}
